\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
feat: add acronyms, fix credits bug, update pipeline
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{Oxidation states}
The questions regarding oxidation states are extracted from the website \url{https://www.cheminfo.org/}. These exercises focus on determining the number of isomers for specific molecules. To perform these calculations, we utilize the RDKit package \cite{bento2020open}.
\subparagraph{Electron count of atoms}
Questions pertaining to the electron count of atoms are gathered from the website \url{https://www.cheminfo.org/}. These inquiries involve determining the electron count of atoms in various chemical contexts. The calculations for these tasks are facilitated using the RDKit package \cite{bento2020open}.
\subparagraph{Number of isomers}
The questions concerning the number of isomers are sourced from the website \url{https://www.cheminfo.org/}. These exercises aim to determine the number of isomers for given molecules. The calculations for these assessments are conducted using the RDKit package \cite{bento2020open}.
\subparagraph{Point group for molecules}
Questions involve predicting the point group for molecules. The ChemCaption tool (\url{https://github.com/lamalab-org/chem-caption/tree/main}) is utilized for data generation. Given a molecule, predict its point group.
\subparagraph{SMILES-IUPAC}
Web scrapped SMILES IUPAC pairs from the PubChem database \cite{pubchem} and then framed questions involve converting SMILES notation to IUPAC nomenclature, utilizing information from the PubChem database.

>>>>

\subparagraph{Oxidation states}
The questions regarding oxidation states are extracted from the website \url{https://www.cheminfo.org/}. These exercises focus on determining the number of isomers for specific molecules. To perform these calculations, we utilize the RDKit package \cite{bento2020open}.
\subparagraph{Electron count of atoms}
Questions pertaining to the electron count of atoms are gathered from the website \url{https://www.cheminfo.org/}. These inquiries involve determining the electron count of atoms in various chemical contexts. The calculations for these tasks are facilitated using the RDKit package \cite{bento2020open}.
\subparagraph{Point group for molecules}
Questions involve predicting the point group for molecules. The ChemCaption tool (\url{https://github.com/lamalab-org/chem-caption/tree/main}) is utilized for data generation. Given a molecule, predict its point group.
\subparagraph{SMILES-IUPAC}
Web scrapped SMILES IUPAC pairs from the PubChem database \cite{pubchem} and then framed questions involve converting SMILES notation to IUPAC nomenclature, utilizing information from the PubChem database.
